Hypertension and microbiome

### 2019-01-01 rrbiome.Rmd
Fixing adonis implementation

```{r function for adnoiscalculation, include = FALSE}
calculateadonis <- function(dset,
                            matrix,
                            responses = list(model_1 = "MAP", model_2 = "SYSTM", model_3 = "DIASM",
                                          model_4 = "PULSEPRESSURE", model_5 = "HYPERTENSION"),
                            covariates = "BL_AGE + SEX",
                            modelstring = "matrix ~ %s + %s",
                            npermutations = 99) {
    ret  <- mclapply(responses, function(response) {
        fo <- as.formula(sprintf(modelstring, response, covariates))
        ad <- adonis(fo, data = dset, permutations = npermutations)
        ad$aov.tab %>% as.data.frame %>%
            tibble::rownames_to_column(var = "response") %>%
            dplyr::mutate(fo = fo)
    }, mc.cores = length(responses))
    data.table::rbindlist(ret, id = "model_name") 
}
```

@@

```{r adonis3, eval = FALSE}
adonis.species %>%
    broom::tidy()

@@

data.table::rbindlist(ret, id = "model_name") %>%
    dplyr::filter(response %in% c("MAP", "SYSTM"))

>>>>

```{r function for adnoiscalculation, include = FALSE}
calculateadonis <- function(dset,
                            matrix,
                            responses = list(model_1 = "MAP", model_2 = "SYSTM", model_3 = "DIASM",
                                          model_4 = "PULSEPRESSURE", model_5 = "HYPERTENSION"),
                            covariates = "BL_AGE + SEX",
                            modelstring = "matrix ~ %s + %s",
                            npermutations = 99) {
    ret  <- mclapply(responses, function(response) {
        fo <- sprintf(modelstring, response, covariates)
        ad <- adonis(as.formula(fo), data = dset, permutations = npermutations)
        ad$aov.tab %>%
            as.data.frame %>%
            tibble::rownames_to_column(var = "term") %>%
            dplyr::mutate(response = response, fo = fo)
      }, mc.cores = length(responses))
    data.table::rbindlist(ret, id = "model_name") %>%
        dplyr::filter(term %in% responses) %>%
            dplyr::select(-term)
}
```

@@

```{r adonis3, eval = FALSE}
 adonis.species <- calculateadonis(dset = meta(pseq.species),
                    matrix = bray.dist.m.species,
                    covariates = "BL_AGE + SEX",
                    npermutations = 2)

 adonis.species

@@

data.table::rbindlist(ret, id = "model_name") %>%
    dplyr::filter(response %in% list(a = "MAP", b = "SYSTM"))
